RDF Validation Requirements - Evaluation and Logical Underpinning

### 2015-01-07 paper/RDF validation requirements/RDF validation requirements.tex

\begin{itemize}
	\item R-205-VARYING-LEVELS-OF-ERROR
	\item R-135-CONSTRAINT-LEVELS
	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
	\item R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS
\end{itemize}

\begin{itemize}
  \item Different levels of severity, priority
	\item validation levels: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraints
\end{itemize}

>>>>

\ms{Validation Levels} corresponds to the requirements

\begin{itemize}
	\item \ms{R-205-VARYING-LEVELS-OF-ERROR},
	\item \ms{R-135-CONSTRAINT-LEVELS},
	\item \ms{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}, and
	\item \ms{R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS}.
\end{itemize}

Different levels of severity, priority should be assigned to constraints.
Possible validation levels could be: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this).
